R MINOS Lineplot Notebooks

### 2023-07-07 minos/outcomes/make_lineplots_all.Rmd
updating lineplot notebook to run on bash and nice pdfs

IMPORTANT NOTE TO RUN PYTHON YOU NEED TO SET THE PYTHON INTERPRETER 
IN TOOLS>GLOBAL_OPTIIONS>PYTHON>CONDA_INTERPRETERS. 
NOT SURE THIS IS NEEDED ANYMORE GIVEN WE'RE SETTING THE CONDA ENV MANUALLY.

Can just use minos_conda or create a miniconda env using reticulate package.

@@

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
knitr::knit_engines$set(python = reticulate::eng_python)
reticulate::use_condaenv("minos_conda", required = FALSE)
```

@@

```{r }
knitr::include_graphics(here::here("plots", "baseline_all_child_uplift_SF_12_aggs_by_year.png"), error=FALSE)
```

@@

```{r }
knitr::include_graphics(here::here("plots", "baseline_poverty_child_uplift_SF_12_aggs_by_year.png"), error=FALSE)
```

@@

```{r }
knitr::include_graphics(here::here("plots", "baseline_living_wage_SF_12_aggs_by_year.png"), error=FALSE)
```

@@

```{r }
knitr::include_graphics(here::here("plots", "baseline_energy_downlift_SF_12_aggs_by_year.png"), error=FALSE)
```

@@

```{r }
knitr::include_graphics(here::here("plots", "all_five_combined_SF_12_aggs_by_year.png"), error=FALSE)
```

>>>>

IMPORTANT NOTE TO RUN THIS NOTEBOOK YOU NEED TO INSTALL THE MINOS_CONDA conda environment for MINOS. 
Can just use minos_conda or create a miniconda env using reticulate package.

@@

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
reticulate::use_condaenv("minos_conda", required = TRUE)
#knitr::knit_engines$set(python = reticulate::eng_python)
#reticulate::py_config()

```

@@

```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
knitr::include_graphics(here::here("plots", "baseline_all_child_uplift_SF_12_aggs_by_year.pdf"), error=FALSE)
```

@@

```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
knitr::include_graphics(here::here("plots", "baseline_poverty_child_uplift_SF_12_aggs_by_year.pdf"), error=FALSE)
```

@@

```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
knitr::include_graphics(here::here("plots", "baseline_living_wage_SF_12_aggs_by_year.pdf"), error=FALSE)
```

@@

```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
knitr::include_graphics(here::here("plots", "baseline_energy_downlift_SF_12_aggs_by_year.pdf"), error=FALSE)
```

@@

```{r out.height = "600px", out.width='800px', include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
knitr::include_graphics(here::here("plots", "all_five_combined_SF_12_aggs_by_year.pdf"), error=FALSE)
```
